Flow-Directed Trace Analysis for Post-Silicon Validation

### 2015-08-19 paper.tex
changed graph

For this model, we consider the flow specification describing the cache coherence protocol supported in GEM5 that is used to build the model in Fig~\ref{SoC}.  This specification consists of two flows, one for cache coherent read requests and one for  cache coherent write requests, from CPUs.  Two such flows describe the cache coherent protocol for each CPU.  As there are two CPUs in this model, there are actually four such flows considered for this model.  More detailed information about the flow specification can be found at \red{github???}

@@

In order to trigger cache coherence protocols, a simple two-threaded program including one producer and one consumer is created and executed on the CPUs, each of which executes one thread.  \red{How is shared memory is simulated???}  GEM5 does not support true concurrency.  When there are two programs running on the CPUs, GEM5 alternates the executions between the two  CPUs.

>>>>

For this model, we consider the flow specification describing the cache coherence protocol supported in GEM5 that is used to build the model in Fig~\ref{SoC}.  This specification consists of two flows, one for cache coherent read requests and one for  cache coherent write requests, from CPUs.  Two such flows describe the cache coherent protocol for each CPU.  As there are two CPUs in this model, there are actually four such flows considered for this model.  
%More detailed information about the flow specification is explained in the following section.

%found at \red{github???}

@@

In order to trigger cache coherence protocols, a simple two-threaded program including one producer and one consumer is created and executed on the CPUs, each of which executes one thread.  \red{How is shared memory is simulated???} . The producer will write to a specified memory address, and the consumer will read from the same address. GEM5 does not support true concurrency.  When there are two programs running on the CPUs, GEM5 alternates the executions between the two  CPUs.
